---
title: "UP_Assignment_Three"
output: html_document
date: "2024-02-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"  

```{r reading the data from the url into a data frame named "college_majors}

college_majors<- data.frame(read.csv(url("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv")))
```

```{r selecting the majors with the words "data" and "statistics"}
data_majors<- college_majors$Major[grep("DATA", college_majors$Major)] 
statistics_majors<- college_majors$Major[grep("STATISTICS", college_majors$Major)]

data_majors
statistics_majors
```

#2 Write code that transforms the data below:
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"
Into a format like this:
c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r converting the string with the list of fruits into character values}

fruit<- c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

fruits = as.character(fruit) 
fruits
```

#3 Describe, in words, what these expressions will match:
(.)\1\1 The same character will be shown three times 
"(.)(.)\\2\\1" Two of the same characters connected to each other will be backwards
(..)\1 Two characters of any value will be repeated 
"(.).\\1.\\1" A single character will be shown three times and there will be a different character between each original one 
"(.)(.)(.).*\\3\\2\\1" Three characters will be shown, then no characters, and then the three original characters backwards   

#4 Construct regular expressions to match words that:
Start and end with the same character.
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

```{r installing and loading the package "stringr"}

install.packages("stringr",repos = "http://cran.us.r-project.org")
library("stringr")
```

```{r creating a list of 10 words}

words<- c("measurement", "gene", "bird", "procedure", "singer", "two", "power", "cabinet", "attitude", "magazine")
```

```{r Constructing a regular expression to match words that start and end with the same character}

same_char_start_and_end<- str_subset(words, "^(.)((.*\\1$)|\\1?$)") 
same_char_start_and_end
```

```{r Constructing a regular expression to match words that contain a repeated pair of letters}

repeated_letters<- str_subset(words, "([A-Za-z][A-Za-z]).*\\1")
repeated_letters
```

```{r Constructing a regular expression to match words that contain one letter repeated in at least three places}

three_repeats<- str_subset(words, "([A-Za-z]).*\\1.*\\1")
three_repeats
```
