---
title: "UP_Week_7"
author: "Ursula Podosenin"
date: "2024-03-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Week Seven Assignment 


```{r}

# Load the necessary libraries
install.packages("xml2", repos = "http://cran.us.r-project.org")
library(xml2)
install.packages("XML", repos = "http://cran.us.r-project.org" )
library(XML)
install.packages("jsonlite", repos = "http://cran.us.r-project.org")
library(jsonlite)
install.packages("rvest", repos = "http://cran.us.r-project.org")
library(rvest)
```

## HTML

```{r}

# Loading the HTML file into a data frame called "html_file"
html_file <- "https://raw.githubusercontent.com/ursulapodosenin/DAT-607/main/Sheet1.html"
html_data <- read_html(html_file)

# Reading the HTML file into a data frame
html_table <- html_data |>
  html_nodes("table") |>
    html_table(fill = TRUE)
books_df_html <- html_table[[1]]

# Final result
books_df_html
```

## XML

```{r}

# Loading the XML file into a data frame called "xml_file"
xml_URL <- "https://raw.githubusercontent.com/ursulapodosenin/DAT-607/main/book_two.xml"
xmlContent <- read_xml(xml_URL)

# Taking the data from the XML file and putting it into a data frame
booksXML <- xmlParse(xmlContent)
booksXML <- xmlToDataFrame(booksXML)
as.data.frame(booksXML)

# Final result 
booksXML
```

## JSON

```{r}
# Loading the JSON file into a data frame called "json_file"
json_file <- "https://raw.githubusercontent.com/ursulapodosenin/DAT-607/main/Book_Data_Three%20-%20Sheet1.json"


# Taking the data from the JSOn file and putting it into a data frame
json_data <- jsonlite::fromJSON(json_file)
books_df_json <- as.data.frame(json_data)

# Final result
books_df_json
```

### Are the three data frames identical?

The three data frames are not entirely identical as the HTML file did not make the variable names of each column as as the headers. Additionally, the XML file interprets the numeric values as characters while the JSON file recognizes the numbers as integers and decimals. The JSON format provides the most accurate and interpretable data frame of all three formats.
